### 2023-08-23 paper/sec-results.tex
sect 3.2

Selection of the {\sc\small xFitter} results for the NNPDF case.

Fig.~\ref{fig:nnpdf40_fasernu2_baseline} presents the same comparison
as in Fig.~\ref{fig:profiling_syst} now for
 the fits
 based on the NNPDF4.0 global analysis.
 %
 The impact on the PDFs found by direct inclusion of the FPF structure
 functions on the NNPDF4.0 fit is qualitatively consistent with
 that found from the Hessian profiling of PDF4LHC21.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q100gev.pdf}
\caption{
The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
%
The FASER$\nu$2 impact projections are provided both without and with systematic
uncertainties accounted for.
%
We include  both  inclusive and charm-tagged structure functions
and assume outgoing lepton charge-separation.
%
}
\label{fig:NNPDF40_baseline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q1p65gev-abs.pdf}
\caption{
The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
%
The FASER$\nu$2 impact projections are provided both without and with systematic
uncertainties accounted for.
%
We include  both  inclusive and charm-tagged structure functions
and assume outgoing lepton charge-separation.
%
}
\label{fig:NNPDF40_lowQ_abs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Add also statistical estimators, and plots of PDF uncertainty only.
%
Maybe also reduction of PDF luminosities, as relevant for phenomenology.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
\caption{Comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variant which includes
  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.
%
}
\label{fig:nnpdf40_fpf_lumis}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

As discussed in Sect.~\ref{subsec:pdf_impact_assessment}, the PDF sensitivity
studies of the FPF neutrino data based on the {\sc\small xFitter} profiling
of PDF4LHC21 are complemented by those based on their direct inclusion
in the NNPDF4.0 global analysis.
%
Here we present results for the impact of the combined FPF neutrino
measurements on NNPDF4.0, namely the analogous study of that shown
in Fig.~\ref{fig:FPF_combined} for PDF4LHC21.
%
While we have produced results also the variations studied in
Sect.~\ref{sec:pdf4lhc21} with the NNPDF fitting methodology, the qualitative
findings are compatible with those obtained with {\sc\small xFitter} and
hence it is not necessary to duplicate them here.

Fig.~\ref{fig:NNPDF40_baseline} displays the
same results as Fig.~\ref{fig:FPF_combined} now in the case of the
fits obtained with the NNPDF4.0 fitting methodology.
%
The baseline NNPDF4.0 NNLO analysis is compared
with the results of the fits which include the combined FPF dataset,
in both the statistics-only scenario and for the case
where systematic uncertainties are also accounted for.
%
As in the PDF4LHC21 analysis, the bands indicate the one-sigma PDF uncertainties.
%
Note that we also show results for the charm PDF (bottom right panel), which
in the NNPDF4.0 fit is also determined directly from the data entering
the fit~\cite{Ball:2016neh}.
%
In this way we can determine the possible constraints that neutrino
DIS measurements at the LHC may impose on the intrinsic charm
content of the proton~\cite{Ball:2022qks}.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q100gev.pdf}
\caption{
  Same as Fig.~\ref{fig:FPF_combined} for the results obtained
  using the NNPDF4.0 fitting methodology.
  %
  The baseline NNPDF4.0 NNLO analysis is compared
  with the results of the fits which include the combined FPF dataset
  in both the statistics-only scenario and for the case
  where systematic uncertainties are also accounted for.
  %
  As in the PDF4LHC21 case, the bands indicate the one-sigma PDF uncertainties.
  %
  We now also show results for the charm PDF (bottom right panel), which
  in the NNPDF4.0 fit is also determined directly from the data entering the fit.
%
}
\label{fig:NNPDF40_baseline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From  Fig.~\ref{fig:NNPDF40_baseline} one finds that
the impact on the PDFs found by direct inclusion of the FPF structure
functions on the NNPDF4.0 fit is qualitatively consistent with
that found from the Hessian profiling of PDF4LHC21.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q1p65gev-abs.pdf}
\caption{
  Same as Fig.~\ref{fig:NNPDF40_baseline} now for the absolute PDFs
  at the initial parametrisation scale, $Q=1.65$ GeV, focusing
  on the large-$x$ region.
%
}
\label{fig:NNPDF40_lowQ_abs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The statistical estimators for the NNPDF4.0 NNLO
baseline fit, compared to those in the variations including
the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
%
From top to bottom we indicate total $\chi^2$, average
over replicas of the training and validation figures of merit
$\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
$\chi^2$ for datasets grouped by process.
%
Note that the last row displays the $\chi^2$ obtained for the combined FPF dataset.

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|l|l|l}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & Baseline
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2$ &  \multirow{4}{*}{Global}      &  &    &  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  & &    &     &   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & &     &     & \\
  $\la \chi^2\ra_{\rm rep}$
  & &      &        &   \\
  \midrule
  \multirow{8}{*}{$\chi^2$}
  & DIS neutral-current                     &      &       &      \\
  & DIS charged-current                     &     &       &      \\
  & Drell--Yan (inclusive and one-jet) &     &       &      \\
  & Top-quark pair production               &     &       &      \\
  & Single-top production                   &     &       &      \\
  & Inclusive jet production                &     &       &      \\
  & Dijet production                        &     &       &      \\
  & Direct photon production                 &    &       &      \\
  & FPF (total)                 &  -  &       &      \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to those in the variations including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
  $\chi^2$ for datasets grouped by process.
  %
  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.49\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.49\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.49\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
\caption{Comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variant which includes
  the full set of FPF pseudo-data.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.
%
}
\label{fig:nnpdf40_fpf_lumis}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
